|

### 2024-03-13 chapter_2/src/appendix.qmd
some drafting done

# Change goodness of fit stuff
gm <- list(
  list("raw" = "nobs", "clean" = "Num.Obs.", "fmt" = 1)
  , list("raw" = "r.squared", "clean" = "$R^2$", "fmt" = 2)
  , list("raw" = "waic", "clean" = "WAIC", "fmt" = 2)
)
# Make table
modelsummary(
  list_fitted_split_1
  , coef_map = c(
    "b_mu2_trial_1_red_stimuli" = "Red yard sign (Independent)"
    , "b_mu3_trial_1_red_stimuli" = "Red yard sign (Republican)"
    , "b_mu2_trial_1_blue_stimuli" = "Blue yard sign (Independent)"
    , "b_mu3_trial_1_blue_stimuli" = "Blue yard sign (Republican)"
    , "b_mu2_Intercept" = "Intercept - Independent"
    , "b_mu3_Intercept" = "Intercept - Republican"
    )
  , statistic = "conf.int"
  , conf_level = 0.9
  , gof_map = gm 
  , notes = c(
    "Data source: Pavlovia"
    , "Positive coefficients reflect the logged-odds"
    , "of claiming candidate is not a Democrat."
    , "Numbers inside brackets reflect the 5th and 95th percentile"
    , "of the draws from the posterior distribution."
  )
  , escape = FALSE
  , output = "latex"
)
```

@@

# Change goodness of fit stuff
gm <- list(
  list("raw" = "nobs", "clean" = "Num.Obs.", "fmt" = 1)
  , list("raw" = "r.squared", "clean" = "$R^2$", "fmt" = 2)
  , list("raw" = "waic", "clean" = "WAIC", "fmt" = 2)
)
# Make table
modelsummary(
  list_fitted_split_1_alt
  , coef_map = c(
    "b_trial_1_red_stimuli" = "Red yard sign"
    , "b_trial_1_blue_stimuli" = "Blue yard sign"
    , "b_Intercept[1]" = "Intercept 1"
    , "b_Intercept[2]" = "Intercept 2"
    )
  , statistic = "conf.int"
  , conf_level = 0.9
  , gof_map = gm 
  , notes = c(
    "Data source: Pavlovia"
    , "Positive coefficients reflect the logged-odds"
    , "of claiming candidate is Republican."
    , "Numbers inside brackets reflect the 5th and 95th percentile"
    , "of the draws from the posterior distribution."
  )
  , escape = FALSE
  , output = "latex"
)
```

@@

# Make table
modelsummary(
  list_fitted_split_2
  , coef_map = c(
    "b_trial_1_red_stimuli" = "Red yard sign"
    , "b_trial_1_blue_stimuli" = "Blue yard sign"
    , "b_age" = "Age"
    , "b_trial_1_red_stimuli:age" = "Red yard sign $\\times$ Age"
    , "b_trial_1_blue_stimuli:age" = "Blue yard sign $\\times$ Age"
    , "b_Intercept[1]" = "Intercept 1"
    , "b_Intercept[2]" = "Intercept 2"
    )
  , statistic = "conf.int"
  , conf_level = 0.9
  , gof_map = gm 
  , notes = c(
    "Data source: Pavlovia"
    , "Positive coefficients reflect the logged-odds"
    , " of claiming candidate is Republican."
    , "Numbers inside brackets reflect the 5th and 95th percentile"
    , " of the draws from the posterior distribution."
  )
  , escape = FALSE
  , output = "latex"
)
```

@@

# Make table
modelsummary(
  list_fitted_split_3
  , coef_map = c(
    "b_trial_1_red_stimuli_alt" = "Red yard sign"
    , "b_trial_1_blue_stimuli_alt" = "Blue yard sign"
    , "b_Intercept[1]" = "Intercept 1"
    , "b_Intercept[2]" = "Intercept 2"
  )
  , statistic = "conf.int"
  , conf_level = 0.9
  , gof_map = gm
  , notes = c(
    "Data source: Pavlovia"
    , "Positive coefficients reflect the logged-odds"
    , " of claiming candidate is Republican."
    , "Numbers inside brackets reflect the 5th and 95th percentile"
    , " of the draws from the posterior distribution."
  )
  , escape = FALSE
  , output = "latex"
)
```

@@

# Redefine names
list_fitted_split_4 <- list(
  "Red - Color blindness moderating" = list_fitted[["h_2"]][["red_colorblind"]]
  , "Blue - Color blindness moderating" = list_fitted[["h_2"]][["blue_colorblind"]]
)
# Make table
modelsummary(
  list_fitted_split_4
  , coef_map = c(
    "b_trial_1_red_stimuli" = "Red yard sign"
    , "b_trial_1_blue_stimuli" = "Blue yard sign"
    , "b_trial_1_red_stimuli:color_blind_dummy" = "Red yard sign $\\times$ Color blind"
    , "b_trial_1_blue_stimuli:color_blind_dummy" = "Blue yard sign $\\times$ Color blind"
    , "b_Intercept[1]" = "Intercept 1"
    , "b_Intercept[2]" = "Intercept 2"
  )
  , statistic = "conf.int"
  , conf_level = 0.9
  , gof_map = gm 
  , notes = c(
    "Data source: Pavlovia"
    , "Positive coefficients reflect the logged-odds"
    , " of claiming candidate is Republican."
    , "Numbers inside brackets reflect the 5th and 95th percentile"
    , " of the draws from the posterior distribution."
  )
  , escape = FALSE
  , output = "latex"
)
```

@@

# Change goodness of fit stuff
gm <- list(
  list("raw" = "nobs", "clean" = "Num.Obs.", "fmt" = 1)
  , list("raw" = "r.squared", "clean" = "$R^2$", "fmt" = 2)
  , list("raw" = "waic", "clean" = "WAIC", "fmt" = 2)
)
# Make table
modelsummary(
  model_names
  , coef_map = c(
    "b_mu2_trial_2_red_stimuli" = "Red yard sign (Independent)"
    , "b_mu3_trial_2_red_stimuli" = "Red yard sign (Republican)"
    , "b_mu2_trial_2_blue_stimuli" = "Blue yard sign (Independent)"
    , "b_mu3_trial_2_blue_stimuli" = "Blue yard sign (Republican)"
    , "b_trial_2_red_stimuli_alt" = "Red yard sign"
    , "b_trial_2_blue_stimuli_alt" = "Blue yard sign"
    , "b_mu2_Intercept" = "Intercept - Independent"
    , "b_mu3_Intercept" = "Intercept - Republican"
    , "b_Intercept[1]" = "Intercept 1"
    , "b_Intercept[2]" = "Intercept 2"
    )
  , statistic = "conf.int"
  , conf_level = 0.9
  , gof_map = gm
  , notes = c(
    "Data source: Pavlovia"
    , "Positive coefficients reflect the logged-odds"
    , " of claiming candidate is not a Democrat (Columns 1 and 2) or is a Republican (Column 3)."
    , "Numbers inside brackets reflect the 5th and 95th percentile"
    , " of the draws from the posterior distribution."
  )
  , escape = FALSE
  , output = "latex"
)
```

@@

# Change goodness of fit stuff
gm <- list(
  list("raw" = "nobs", "clean" = "Num.Obs.", "fmt" = 1)
  , list("raw" = "r.squared", "clean" = "$R^2$", "fmt" = 2)
  , list("raw" = "waic", "clean" = "WAIC", "fmt" = 2)
)
# Make table
modelsummary(
  model_names
  , coef_map = c(
    "b_mu2_trial_3_red_stimuli" = "Red yard sign (Independent)"
    , "b_mu3_trial_3_red_stimuli" = "Red yard sign (Republican)"
    , "b_mu2_trial_3_blue_stimuli" = "Blue yard sign (Independent)"
    , "b_mu3_trial_3_blue_stimuli" = "Blue yard sign (Republican)"
    , "b_trial_3_red_stimuli_alt" = "Red yard sign"
    , "b_trial_3_blue_stimuli_alt" = "Blue yard sign"
    , "b_mu2_Intercept" = "Intercept - Independent"
    , "b_mu3_Intercept" = "Intercept - Republican"
    , "b_Intercept[1]" = "Intercept 1"
    , "b_Intercept[2]" = "Intercept 2"
    )
  , statistic = "conf.int"
  , conf_level = 0.9
  , gof_map = gm 
  , notes = c(
    "Data source: Pavlovia"
    , "Positive coefficients reflect the logged-odds"
    , " of claiming candidate is Republican."
    , "Numbers inside brackets reflect the 5th and 95th percentile"
    , " of the draws from the posterior distribution."
  )
  , escape = FALSE
  , output = "latex"
)
```

@@

# Change goodness of fit stuff
gm <- list(
  list("raw" = "nobs", "clean" = "Num.Obs.", "fmt" = 1)
  , list("raw" = "r.squared", "clean" = "$R^2$", "fmt" = 2)
  , list("raw" = "waic", "clean" = "WAIC", "fmt" = 2)
)
# Make table
modelsummary(
  model_names
  , coef_map = c(
    "b_trial_2_red_stimuli" = "Red yard sign"
    , "b_trial_2_blue_stimuli" = "Blue yard sign"
    , "b_Intercept[1]" = "Intercept 1"
    , "b_Intercept[2]" = "Intercept 2"
    )
  , statistic = "conf.int"
  , conf_level = 0.9
  , gof_map = gm
  , notes = c(
    "Data source: Pavlovia"
    , "Positive coefficients reflect the logged-odds"
    , " of claiming candidate is Republican."
    , "Numbers inside brackets reflect the 5th and 95th percentile"
    , " of the draws from the posterior distribution."
  )
  , escape = FALSE
  , output = "latex"
)
```

@@

# Change goodness of fit stuff
gm <- list(
  list("raw" = "nobs", "clean" = "Num.Obs.", "fmt" = 1)
  , list("raw" = "r.squared", "clean" = "$R^2$", "fmt" = 2)
  , list("raw" = "waic", "clean" = "WAIC", "fmt" = 2)
)
# Make table
modelsummary(
  model_names
  , coef_map = c(
    "b_trial_3_red_stimuli" = "Red yard sign"
    , "b_trial_3_blue_stimuli" = "Blue yard sign"
    , "b_Intercept[1]" = "Intercept 1"
    , "b_Intercept[2]" = "Intercept 2"
    )
  , statistic = "conf.int"
  , conf_level = 0.9
  , gof_map = gm 
  , notes = c(
    "Data source: Pavlovia"
    , "Positive coefficients reflect the logged-odds"
    , " of claiming candidate is Republican."
    , "Numbers inside brackets reflect the 5th and 95th percentile"
    , " of the draws from the posterior distribution."
  )
  , escape = FALSE
  , output = "latex"
)
```

@@

# Make table
modelsummary(
  model_names
  , coef_map = c(
    "b_trial_1_red_stimuli" = "Red yard sign"
    , "b_trial_1_blue_stimuli" = "Blue yard sign"
    , "b_pid_7" = "Party ID"
    , "b_trial_1_red_stimuli:pid_7" = "Red yard sign $\\times$ Party ID"
    , "b_trial_1_blue_stimuli:pid_7" = "Blue yard sign $\\times$ Party ID"
    , "b_attention" = "Attention"
    , "b_age" = "Age"
    , "b_gender_idMale" = "Gender - Male"
    , "b_gender_idNonMbinary" = "Gender - Non-binary"
    , "b_gender_idPrefernottochoose" = "Gender - Prefer not to choose"
    , "b_race_idBlacknonMhispanic" = "Black"
    , "b_race_idHispanice" = "Hispanic"
    , "b_race_idMultipleraces" = "Multiple races"
    , "b_race_idNativeAmericanDAlaskaNativeOrOtherRace" = "Other race"
    , "b_race_idWhitenonMhispanic" = "White"
  )  
  , statistic = "conf.int"
  , conf_level = 0.9
  , gof_map = gm 
  , notes = c(
    "Data source: Pavlovia"
    , "Positive coefficients reflect the logged-odds"
    , " of claiming candidate is Republican."
    , "Numbers inside brackets reflect the 5th and 95th percentile"
    , " of the draws from the posterior distribution."
  )
  , escape = FALSE
  , output = "latex"
)
```

@@

```{r}
#| label: tbl-h-4-dispersion
#| tbl-cap: Checking for over-dispersion of data
df_over_dispersed <- list_df[["cleaned"]][, c("trial_1_time_elapsed")]
names(df_over_dispersed)[names(df_over_dispersed) == 'trial_1_time_elapsed'] <- 'Time Elapsed'
datasummary_skim(
  df_over_dispersed
  , notes = "Data source: Prolific sample."
  , histogram = FALSE
)
```

@@

df_study_2_subset <- df_study_2[, c('% Red', '% Blue', '% White')]
datasummary_skim(
  df_study_2_subset
  , notes = "Data source: CAPD Yard Signs."
  , histogram = FALSE
)

@@

```{r}
#| label: tbl-hypothesis-5
#| tbl-cap: The effect of democratic vote share on color choices for yard sign
list_fitted[["h_5"]] <- list_fitted[["h_5"]][c(1,2)]
names(list_fitted[["h_5"]]) <- c("Prop. yard sign Red", "Prop. yard sign Blue")
modelsummary(
  list_fitted[["h_5"]]
  , stat = "conf.int"
  , conf_level = 0.9
  , metrics = c("n.obs", "RMSE")
  , coef_map = c(
    "b_dem_vote_share" = "Democratic vote share (percent)"
    , "b_Intercept" = "Intercept"
  )
  , notes = c(
    "Data source: Center for Political Design and MIT Election Lab"
    , "Positive coefficients reflect the logged-odds"
    , "of claiming candidate is Republican."
    , "Numbers inside brackets reflect the 5th and 95th percentile"
    , "of the draws from the posterior distribution."
  )
  , escape = FALSE
  , output = "latex"
)
```

>>>>

# Change goodness of fit stuff
gm <- list(
  list("raw" = "nobs", "clean" = "Num.Obs.", "fmt" = 1)
  , list("raw" = "r.squared", "clean" = "$R^2$", "fmt" = 2)
  , list("raw" = "waic", "clean" = "WAIC", "fmt" = 2)
)
# Make table
modelsummary(
  list_fitted_split_1
  , coef_map = c(
    "b_mu2_trial_1_red_stimuli" = "Red yard sign (Independent)"
    , "b_mu3_trial_1_red_stimuli" = "Red yard sign (Republican)"
    , "b_mu2_trial_1_blue_stimuli" = "Blue yard sign (Independent)"
    , "b_mu3_trial_1_blue_stimuli" = "Blue yard sign (Republican)"
    , "b_mu2_Intercept" = "Intercept - Independent"
    , "b_mu3_Intercept" = "Intercept - Republican"
    )
  , statistic = "conf.int"
  , conf_level = 0.9
  , gof_map = gm 
  , notes = c(
    "Data source: Pavlovia"
    , "Positive coefficients reflect the logged-odds"
    , "of claiming candidate is not a Democrat."
    , "Numbers inside brackets reflect the 5th and 95th percentile"
    , "of the draws from the posterior distribution."
  )
  , escape = FALSE
  , output = "markdown"
)
```

@@

# Change goodness of fit stuff
gm <- list(
  list("raw" = "nobs", "clean" = "Num.Obs.", "fmt" = 1)
  , list("raw" = "r.squared", "clean" = "$R^2$", "fmt" = 2)
  , list("raw" = "waic", "clean" = "WAIC", "fmt" = 2)
)
# Make table
modelsummary(
  list_fitted_split_1_alt
  , coef_map = c(
    "b_trial_1_red_stimuli" = "Red yard sign"
    , "b_trial_1_blue_stimuli" = "Blue yard sign"
    , "b_Intercept[1]" = "Intercept 1"
    , "b_Intercept[2]" = "Intercept 2"
    )
  , statistic = "conf.int"
  , conf_level = 0.9
  , gof_map = gm 
  , notes = c(
    "Data source: Pavlovia"
    , "Positive coefficients reflect the logged-odds"
    , "of claiming candidate is Republican."
    , "Numbers inside brackets reflect the 5th and 95th percentile"
    , "of the draws from the posterior distribution."
  )
  , escape = FALSE
  , output = "markdown"
)
```

@@

# Make table
modelsummary(
  list_fitted_split_2
  , coef_map = c(
    "b_trial_1_red_stimuli" = "Red yard sign"
    , "b_trial_1_blue_stimuli" = "Blue yard sign"
    , "b_age" = "Age"
    , "b_trial_1_red_stimuli:age" = "Red yard sign $\\times$ Age"
    , "b_trial_1_blue_stimuli:age" = "Blue yard sign $\\times$ Age"
    , "b_Intercept[1]" = "Intercept 1"
    , "b_Intercept[2]" = "Intercept 2"
    )
  , statistic = "conf.int"
  , conf_level = 0.9
  , gof_map = gm 
  , notes = c(
    "Data source: Pavlovia"
    , "Positive coefficients reflect the logged-odds"
    , " of claiming candidate is Republican."
    , "Numbers inside brackets reflect the 5th and 95th percentile"
    , " of the draws from the posterior distribution."
  )
  , escape = FALSE
  , output = "markdown"
)
```

@@

# Make table
modelsummary(
  list_fitted_split_3
  , coef_map = c(
    "b_trial_1_red_stimuli_alt" = "Red yard sign"
    , "b_trial_1_blue_stimuli_alt" = "Blue yard sign"
    , "b_Intercept[1]" = "Intercept 1"
    , "b_Intercept[2]" = "Intercept 2"
  )
  , statistic = "conf.int"
  , conf_level = 0.9
  , gof_map = gm
  , notes = c(
    "Data source: Pavlovia"
    , "Positive coefficients reflect the logged-odds"
    , " of claiming candidate is Republican."
    , "Numbers inside brackets reflect the 5th and 95th percentile"
    , " of the draws from the posterior distribution."
  )
  , escape = FALSE
  , output = "markdown"
)
```

@@

# Redefine names
list_fitted_split_4 <- list(
  "Red - Color blindness moderating" = list_fitted[["h_2"]][["red_colorblind"]]
  , "Blue - Color blindness moderating" = list_fitted[["h_2"]][["blue_colorblind"]]
)
# Make table
modelsummary(
  list_fitted_split_4
  , coef_map = c(
    "b_trial_1_red_stimuli" = "Red yard sign"
    , "b_trial_1_blue_stimuli" = "Blue yard sign"
    , "b_trial_1_red_stimuli:color_blind_dummy" = "Red yard sign $\\times$ Color blind"
    , "b_trial_1_blue_stimuli:color_blind_dummy" = "Blue yard sign $\\times$ Color blind"
    , "b_Intercept[1]" = "Intercept 1"
    , "b_Intercept[2]" = "Intercept 2"
  )
  , statistic = "conf.int"
  , conf_level = 0.9
  , gof_map = gm 
  , notes = c(
    "Data source: Pavlovia"
    , "Positive coefficients reflect the logged-odds"
    , " of claiming candidate is Republican."
    , "Numbers inside brackets reflect the 5th and 95th percentile"
    , " of the draws from the posterior distribution."
  )
  , escape = FALSE
  , output = "markdown"
)
```

@@

# Change goodness of fit stuff
gm <- list(
  list("raw" = "nobs", "clean" = "Num.Obs.", "fmt" = 1)
  , list("raw" = "r.squared", "clean" = "$R^2$", "fmt" = 2)
  , list("raw" = "waic", "clean" = "WAIC", "fmt" = 2)
)
# Make table
modelsummary(
  model_names
  , coef_map = c(
    "b_mu2_trial_2_red_stimuli" = "Red yard sign (Independent)"
    , "b_mu3_trial_2_red_stimuli" = "Red yard sign (Republican)"
    , "b_mu2_trial_2_blue_stimuli" = "Blue yard sign (Independent)"
    , "b_mu3_trial_2_blue_stimuli" = "Blue yard sign (Republican)"
    , "b_trial_2_red_stimuli_alt" = "Red yard sign"
    , "b_trial_2_blue_stimuli_alt" = "Blue yard sign"
    , "b_mu2_Intercept" = "Intercept - Independent"
    , "b_mu3_Intercept" = "Intercept - Republican"
    , "b_Intercept[1]" = "Intercept 1"
    , "b_Intercept[2]" = "Intercept 2"
    )
  , statistic = "conf.int"
  , conf_level = 0.9
  , gof_map = gm
  , notes = c(
    "Data source: Pavlovia"
    , "Positive coefficients reflect the logged-odds"
    , " of claiming candidate is not a Democrat (Columns 1 and 2) or is a Republican (Column 3)."
    , "Numbers inside brackets reflect the 5th and 95th percentile"
    , " of the draws from the posterior distribution."
  )
  , escape = FALSE
  , output = "markdown"
)
```

@@

# Change goodness of fit stuff
gm <- list(
  list("raw" = "nobs", "clean" = "Num.Obs.", "fmt" = 1)
  , list("raw" = "r.squared", "clean" = "$R^2$", "fmt" = 2)
  , list("raw" = "waic", "clean" = "WAIC", "fmt" = 2)
)
# Make table
modelsummary(
  model_names
  , coef_map = c(
    "b_mu2_trial_3_red_stimuli" = "Red yard sign (Independent)"
    , "b_mu3_trial_3_red_stimuli" = "Red yard sign (Republican)"
    , "b_mu2_trial_3_blue_stimuli" = "Blue yard sign (Independent)"
    , "b_mu3_trial_3_blue_stimuli" = "Blue yard sign (Republican)"
    , "b_trial_3_red_stimuli_alt" = "Red yard sign"
    , "b_trial_3_blue_stimuli_alt" = "Blue yard sign"
    , "b_mu2_Intercept" = "Intercept - Independent"
    , "b_mu3_Intercept" = "Intercept - Republican"
    , "b_Intercept[1]" = "Intercept 1"
    , "b_Intercept[2]" = "Intercept 2"
    )
  , statistic = "conf.int"
  , conf_level = 0.9
  , gof_map = gm 
  , notes = c(
    "Data source: Pavlovia"
    , "Positive coefficients reflect the logged-odds"
    , " of claiming candidate is Republican."
    , "Numbers inside brackets reflect the 5th and 95th percentile"
    , " of the draws from the posterior distribution."
  )
  , escape = FALSE
  , output = "markdown"
)
```

@@

# Change goodness of fit stuff
gm <- list(
  list("raw" = "nobs", "clean" = "Num.Obs.", "fmt" = 1)
  , list("raw" = "r.squared", "clean" = "$R^2$", "fmt" = 2)
  , list("raw" = "waic", "clean" = "WAIC", "fmt" = 2)
)
# Make table
modelsummary(
  model_names
  , coef_map = c(
    "b_trial_2_red_stimuli" = "Red yard sign"
    , "b_trial_2_blue_stimuli" = "Blue yard sign"
    , "b_Intercept[1]" = "Intercept 1"
    , "b_Intercept[2]" = "Intercept 2"
    )
  , statistic = "conf.int"
  , conf_level = 0.9
  , gof_map = gm
  , notes = c(
    "Data source: Pavlovia"
    , "Positive coefficients reflect the logged-odds"
    , " of claiming candidate is Republican."
    , "Numbers inside brackets reflect the 5th and 95th percentile"
    , " of the draws from the posterior distribution."
  )
  , escape = FALSE
  , output = "markdown"
)
```

@@

# Change goodness of fit stuff
gm <- list(
  list("raw" = "nobs", "clean" = "Num.Obs.", "fmt" = 1)
  , list("raw" = "r.squared", "clean" = "$R^2$", "fmt" = 2)
  , list("raw" = "waic", "clean" = "WAIC", "fmt" = 2)
)
# Make table
modelsummary(
  model_names
  , coef_map = c(
    "b_trial_3_red_stimuli" = "Red yard sign"
    , "b_trial_3_blue_stimuli" = "Blue yard sign"
    , "b_Intercept[1]" = "Intercept 1"
    , "b_Intercept[2]" = "Intercept 2"
    )
  , statistic = "conf.int"
  , conf_level = 0.9
  , gof_map = gm 
  , notes = c(
    "Data source: Pavlovia"
    , "Positive coefficients reflect the logged-odds"
    , " of claiming candidate is Republican."
    , "Numbers inside brackets reflect the 5th and 95th percentile"
    , " of the draws from the posterior distribution."
  )
  , escape = FALSE
  , output = "markdown"
)
```

@@

# Make table
modelsummary(
  model_names
  , coef_map = c(
    "b_trial_1_red_stimuli" = "Red yard sign"
    , "b_trial_1_blue_stimuli" = "Blue yard sign"
    , "b_pid_7" = "Party ID"
    , "b_trial_1_red_stimuli:pid_7" = "Red yard sign $\\times$ Party ID"
    , "b_trial_1_blue_stimuli:pid_7" = "Blue yard sign $\\times$ Party ID"
    , "b_attention" = "Attention"
    , "b_age" = "Age"
    , "b_gender_idMale" = "Gender - Male"
    , "b_gender_idNonMbinary" = "Gender - Non-binary"
    , "b_gender_idPrefernottochoose" = "Gender - Prefer not to choose"
    , "b_race_idBlacknonMhispanic" = "Black"
    , "b_race_idHispanice" = "Hispanic"
    , "b_race_idMultipleraces" = "Multiple races"
    , "b_race_idNativeAmericanDAlaskaNativeOrOtherRace" = "Other race"
    , "b_race_idWhitenonMhispanic" = "White"
  )  
  , statistic = "conf.int"
  , conf_level = 0.9
  , gof_map = gm 
  , notes = c(
    "Data source: Pavlovia"
    , "Positive coefficients reflect the logged-odds"
    , " of claiming candidate is Republican."
    , "Numbers inside brackets reflect the 5th and 95th percentile"
    , " of the draws from the posterior distribution."
  )
  , escape = FALSE
  , output = "markdown"
)
```

@@

```{r}
#| label: tbl-h-4-dispersion
#| tbl-cap: Checking for over-dispersion of data
df_over_dispersed <- list_df[["cleaned"]][, c("trial_1_time_elapsed")]
names(df_over_dispersed)[names(df_over_dispersed) == 'trial_1_time_elapsed'] <- 'Time Elapsed'
datasummary_skim(
  df_over_dispersed
  , notes = "Data source: Prolific sample."
  , histogram = FALSE
  , output = "markdown"
)
```

@@

df_study_2_subset <- df_study_2[, c('% Red', '% Blue', '% White')]
datasummary_skim(
  df_study_2_subset
  , notes = "Data source: CAPD Yard Signs."
  , histogram = FALSE
  , output = "markdown"
)

@@

```{r}
#| label: tbl-hypothesis-5
#| tbl-cap: The effect of democratic vote share on color choices for yard sign
list_fitted[["h_5"]] <- list_fitted[["h_5"]][c(1,2)]
names(list_fitted[["h_5"]]) <- c("Prop. yard sign Red", "Prop. yard sign Blue")
modelsummary(
  list_fitted[["h_5"]]
  , stat = "conf.int"
  , conf_level = 0.9
  , metrics = c("n.obs", "RMSE")
  , coef_map = c(
    "b_dem_vote_share" = "Democratic vote share (percent)"
    , "b_Intercept" = "Intercept"
  )
  , notes = c(
    "Data source: Center for Political Design and MIT Election Lab"
    , "Positive coefficients reflect the logged-odds"
    , "of claiming candidate is Republican."
    , "Numbers inside brackets reflect the 5th and 95th percentile"
    , "of the draws from the posterior distribution."
  )
  , escape = FALSE
  , output = "markdown"
)
```
